%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Oliver Wyman: Digital} % Organization
    {Boston, Massachusetts} % Location
    {October 2017 - Present} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Containerization and CI/CD specialist: modifying a diverse group of ten-plus projects to build and deploy continuously in containers as microservices.
        \item Data as code: advocate and developer for migration-based database deployments. Introduced the team to a framework around Alembic that decreased build time and eliminated down-time of their deployments, with arbitrarily scaling full-CI/CD\@.
        \item Refactoring rough, hard-coded Python app to full portability, regular client delivery, and of course with proper CI/CD\@.
        \item Realized our auth system could be modularized as a drop-in solution for our legacy applications \- implemented it, picking up Express along the way.
        \item Spear-headed project to continuously collect, track, and present data about our consulting organization's projects and assets. Surfacing forgotten items, decreasing the Sustaining organization's seek time, and bringing InfoSec auditability.
      \end{cvitems}
    }
    \begin{cventryskills}
      \item Python
      \item Docker
      \item Jenkins Pipelines
      \item Rancher
      \item Node.js (Express \& Vue)
      \item Flask
      \item Alembic
      \item MS SQL Server
      \item PostgreSQL
      \item GraphQL
      \item Linux
      \item Confluence
    \end{cventryskills}

%---------------------------------------------------------
  \cventry
    {Software Engineer - Orion: NASA's next manned spacecraft} % Job title
    {Lockheed Martin: Space Systems} % Organization
    {Littleton, Colorado} % Location
    {September 2014 - Present} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Principle architect in moving Orion ground software testing from pen and paper to full automation with Pytest.}
        \item {Built a Python/LaTeX engine for creating NASA deliverables.  Now engineers compile these deliverables the day - saving them a month or more of manual paperwork, per deliverable.}
        \item {Advised the flight software verification automation tiger team, sharing the knowledge and processes established while automating ground software.}
        \item {Built a recursive-descent compiler for a templating language similar to Jinja2.}
        \item {Verified software requirements for NASA.}
        \item {Voltunteered for Code Quest, Lockheed Martin's computer programming competition for high school teams.}
      \end{cvitems}
    }
    \begin{cventryskills}
      \item Python
      \item LaTeX
      \item Sphinx
      \item Linux
      \item Vim
      \item Perforce
      \item JIRA
      \item Jenkins
      \item Confluence
      \item Agile
      \item Test-driven development
      \item ELK (Elasticsearch, Logstash, Kibana)
    \end{cventryskills}

%---------------------------------------------------------
  \cventry
    {Network Administrator} % Job title
    {Air Sciences, Inc.} % Organization
    {Golden, Colorado} % Location
    {November 2011 - March 2014} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Purchased, set up, and maintained servers, laptops, and networks for a 50 person company.}
        \item {Introduced new processes such as a ticketing system, wiki, and KVM virtual machines.}
        \item {Interviewed and trained three new administrators.}
      \end{cvitems}
    }
    \begin{cventryskills}
      \item Django
      \item Git
      \item Mediawiki
      \item Network configuration
      \item Linux administration
      \item User support
    \end{cventryskills}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {CSM Alumni Association} % Organization
    {Golden, Colorado} % Location
    {August 2010 - April 2014} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web Development: website design, web app, newsletter, graphics, audio, and video.}
        \item {Data Specialist: updated and maintained alumni records database.}
      \end{cvitems}
    }
    \begin{cventryskills}
      \item Django
      \item Wordpress
      \item PHP
      \item HTML/CSS
      \item Audacity audio editing
      \item GIMP image manipulation
      \item Web design
    \end{cventryskills}

%---------------------------------------------------------
  \cventry
    {Web Designer/Developer{\enskip\cdotp\enskip}Administrator} % Job title
    {Independent Consultant} % Organization
    {} % Location
    {2009 - Present} % Date(s)
    {%
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Network and client workstation administration and set up.}
        \item {Website design, development, and deployment.}
      \end{cvitems}
    }
    \begin{cventryskills}
      \item Web design \& development
      \item Git
      \item Shared hosting
      \item User support
      \item MacOS
    \end{cventryskills}

%---------------------------------------------------------
\end{cventries}
